\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-01-26 doc/chapters/usage.tex
write a workflow section and correcting ./createmodel usage

\section{Usage}
\subsection{Files and directories}

@@

\subsubsection{\code{createmodel}}

The \code{createmodel} script sets up a \flexisusy\ model.  This involves
%
\begin{itemize}
\item a model directory \code{models/<flexiblesusy-model>/}
\item a makefile module \code{models/<flexiblesusy-model>/module.mk}
\item a \flexisusy\ model file \code{models/<flexiblesusy-model>/FlexibleSUSY.m}
\item a Mathematica start script \code{models/<flexiblesusy-model>/start.m}
\end{itemize}
%
Usage:
\begin{lstlisting}[language=bash]
./createmodel --models=<flexiblesusy-model>:<sarah-model>
\end{lstlisting}
Here \code{<flexiblesusy-model>} is the name of \flexisusy\ model
to be created and \code{<sarah-model>} is the name of the \sarah\
model file which defines the Lagrangian and the particles.\\
Example:
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM
\end{lstlisting}
%
Multiple models can be created at once by separating the models by a
comma.\\
Example:
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM,MyCNMSSM:NMSSM
\end{lstlisting}
%
If a certain \sarah\ sub-model should be used, the name of the sub-model
has to be appended with at preceeding slash.\\
Example: use the \code{CKM} sub-model of the \code{MSSM}
\begin{lstlisting}[language=bash]
./createmodel --models=MyCMSSM:MSSM/CKM
\end{lstlisting}
%
For further information and options see
\begin{lstlisting}[language=bash]
./createmodel --help
\end{lstlisting}

\subsubsection{\code{configure}}

@@

\subsection{Model files}

@@

\subsection{Makefile modules}

>>>>

\section{Usage}

\subsection{Workflow}

Creating a spectrum generator with \flexisusy consists of the
following steps:
%
\begin{enumerate}
\item Creating a \emph{SARAH model file}.  Note, that SARAH already
  ships a lot of pre-defined model files in \code{SARAH/Models/} that
  can be used.
\item Creating a \emph{\flexisusy model file} in
  \code{models/<model-name>/}.  The \code{createmodel} script will
  help you creating one, see Section~\ref{sec:createmodel}.  For more
  details on how to write a \flexisusy model file see
  Section~\ref{sec:model-files}.
\item \emph{Configure} \flexisusy with your desired model, see
  Section~\ref{sec:configure}.
\item Run \code{make}.  This will create the C++ code for your
  spectrum generator and compile it, see Section~\ref{sec:make}.
\end{enumerate}

\subsection{Files and directories}

@@

\subsubsection{\code{createmodel}}
\label{sec:createmodel}

The \code{createmodel} script sets up a \flexisusy\ model.  This involves
%
\begin{itemize}
\item a model directory \code{models/<flexiblesusy-model>/}
\item a makefile module \code{models/<flexiblesusy-model>/module.mk}
\item a \flexisusy\ model file \code{models/<flexiblesusy-model>/FlexibleSUSY.m}
\item a Mathematica start script \code{models/<flexiblesusy-model>/start.m}
\end{itemize}
%
Usage:
\begin{lstlisting}[language=bash]
./createmodel --name=<flexiblesusy-model> --sarah-model=<sarah-model>
\end{lstlisting}
Here \code{<flexiblesusy-model>} is the name of \flexisusy\ model
to be created and \code{<sarah-model>} is the name of the \sarah\
model file which defines the Lagrangian and the particles.\\
Example:
\begin{lstlisting}[language=bash]
./createmodel --name=MyCMSSM --sarah-model=MSSM
\end{lstlisting}
%
%
If a certain \sarah\ sub-model should be used, the name of the sub-model
has to be appended with at preceeding slash.\\
Example: use the \code{CKM} sub-model of the \code{MSSM}
\begin{lstlisting}[language=bash]
./createmodel --name=MyCMSSM --sarah-model=MSSM/CKM
\end{lstlisting}
%
For further information and options see
\begin{lstlisting}[language=bash]
./createmodel --help
\end{lstlisting}

\subsubsection{\code{configure}}
\label{sec:configure}

@@

\subsubsection{\code{make}}
\label{sec:make}

Running \code{make} will create the C++ source code for your spectrum
generator and compile it.  These two processes are controled in the
makefile module \code{models/<model-name>/module.mk}.  See,
Section~\ref{sec:makefile-modules} for details how to create your own
makefile module.

\subsection{Model files}
\label{sec:model-files}

@@

\subsection{Makefile modules}
\label{sec:makefile-modules}
